---
title: "Chinese_topic_Exp.3: Statistical Report"
author: "Fuyun WU "
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chinese topic processing
  - Mandarin: 60id

## Load relevant packages
```{r warning=FALSE}
library(plyr)
library(ggplot2)
library(reshape2)
library(scales) 
library(MASS)
library(lme4)
library(car)
library(languageR)
```

## Import dataset: Exp3 topic w/ contexts 
```{r }
topic3 <- read.csv("topic3_w_context_60id.csv")
```

```{r }
topic3$subj <- as.factor(topic3$subj)
topic3$item <- as.factor(topic3$item)
```

```{r }
boxcox <- boxcox(topic3$RT~ topic3$condition * topic3$subj) 
##lamda peaks at -1, thus use rrt
topic3 <- subset(topic3, topic3$RT > 50 & topic3$ RT < 5000) 
##eliminated 142 (0.82%) datapoints
topic3$rrt <- -1000/topic3$RT
```

###sum-contrast coding
```{r }
order <- ifelse(topic3$condition%in%c("a","c"),-1,1)
complexity <- ifelse(topic3$condition%in%c("a","b"),-1,1)
orderxcomplexity <- ifelse(topic3$condition%in%c("b","c"),-1,1)

topic3$order <- order
topic3$complexity <- complexity
topic3$orderxcomplexity <- orderxcomplexity
head(topic3, n=5)
```

### RC-V2 (by part of speech): 
```{r }
m0.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
                + (1+ order + complexity + orderxcomplexity||subj) 
                + (1 + order + complexity + orderxcomplexity||item), 
                subset(topic3,constituent =="RC-V2"))
summary(m0.RCV2)

m1.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
                + (1+ order + complexity + orderxcomplexity||subj) 
                + (1 |item), 
                subset(topic3,constituent =="RC-V2")) ##optimal model
summary(m1.RCV2)
```

### pos15 (RC-V2): W4 as reported in the paper
```{r }
m0.pos15.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
            + (1+ order + complexity + orderxcomplexity||subj) 
             + (1 + order + complexity + orderxcomplexity||item), 
         subset(topic3,position =="15"))
summary(m0.pos15.RCV2)

m1.pos15.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
         + (1+ order + complexity + orderxcomplexity||subj) 
       + (1 + order + orderxcomplexity||item), 
      subset(topic3,position =="15")) ## optimal model
summary(m1.pos15.RCV2)  
```

## DE: 
```{r }
m0.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
       + (1+ order + complexity + orderxcomplexity||subj) 
     + (1 + order + complexity + orderxcomplexity||item), 
       subset(topic3,constituent =="DE"))
summary(m0.DE)

m1.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order ||subj) 
        + (1 + order + complexity + orderxcomplexity||item), 
        subset(topic3,constituent =="DE"))
summary(m1.DE)

m2.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order ||subj) 
              + (1 + order + complexity||item), 
              subset(topic3,constituent =="DE")) ## optimal model
summary(m2.DE)
```

### pos16,DE: W5 as reported in the paper
```{r }
m0.pos16.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
           + (1+ order + complexity + orderxcomplexity||subj) 
        + (1 + order + complexity + orderxcomplexity||item), 
        subset(topic3,position =="16"))
summary(m0.pos16.DE)

m1.pos16.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
      + (1+ order + complexity + orderxcomplexity||subj) 
         + (1 + order + complexity ||item), 
                    subset(topic3,position =="16"))
summary(m1.pos16.DE)

m2.pos16.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
                    + (1+ order + complexity ||subj) 
                    + (1 + order + complexity ||item), 
                    subset(topic3,position =="16")) ## optimal model
summary(m2.pos16.DE) 
```

### HN: 
```{r }
m0.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order + complexity + orderxcomplexity||subj) 
         + (1 + order + complexity + orderxcomplexity||item), 
         subset(topic3,constituent =="HN"))
summary(m0.HN)

m1.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order + complexity ||subj) 
              + (1 + order + complexity ||item), 
              subset(topic3,constituent =="HN"))
summary(m1.HN)

m2.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1 + complexity ||subj) 
              + (1 + order + complexity ||item), 
              subset(topic3,constituent =="HN")) ## optimal model
summary(m2.HN)
```

### pos17.HN: W6 as reported in the paper
```{r }
m0.pos17.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
         + (1+ order + complexity + orderxcomplexity||subj) 
       + (1 + order + complexity + orderxcomplexity||item), 
         subset(topic3,position =="17"))
summary(m0.pos17.HN)

m1.pos17.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
          + (1+ complexity + orderxcomplexity||subj) 
          + (1 + order + complexity ||item), 
           subset(topic3, position =="17")) ## optimal model
summary(m1.pos17.HN)  
```

### ADV: 
```{r }
m0.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
       + (1+ order + complexity + orderxcomplexity||subj) 
       + (1 + order + complexity + orderxcomplexity||item), 
       subset(topic3,constituent =="ADV"))
summary(m0.ADV)

m1.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order + complexity + orderxcomplexity||subj) 
        + (1 + order + complexity ||item), 
         subset(topic3,constituent =="ADV")) ## optimal model
summary(m1.ADV)
```

#### pos18.ADV: W7 as reported in the paper
```{r }
m0.pos18.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order + complexity + orderxcomplexity||subj) 
        + (1 + order + complexity + orderxcomplexity||item), 
       subset(topic3,position =="18"))
summary(m0.pos18.ADV)

m1.pos18.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
           + (1+ order + complexity + orderxcomplexity||subj) 
           + (1 + order + complexity ||item), 
         subset(topic3,position =="18")) ## optimal model
summary(m1.pos18.ADV)  
```

### quantifier: 
```{r }
m0.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order + complexity + orderxcomplexity||subj) 
         + (1 + order + complexity + orderxcomplexity||item), 
         subset(topic3,constituent =="quantifier"))
summary(m0.quantifier)

m1.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+  complexity + orderxcomplexity||subj) 
      + (1 + order + complexity + orderxcomplexity||item), 
       subset(topic3,constituent =="quantifier")) ## optimal model
summary(m1.quantifier)
```

######pos19.quantifier: W8 as reported in the paper
```{r }
m0.pos19.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
          + (1+ order + complexity + orderxcomplexity||subj) 
          + (1 + order + complexity + orderxcomplexity||item), 
          subset(topic3,position =="19"))
summary(m0.pos19.quantifier)

m1.pos19.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
             + (1+ complexity ||subj) 
            + (1 + complexity ||item), 
        subset(topic3,position =="19"))
summary(m1.pos19.quantifier)  
```

### main-V1: maximal model overfitted; use Order as the fixed effect 
```{r }
xtabs(~order+condition, 
      subset(topic3, constituent == "main-V1"))
xtabs(~complexity+condition, 
      subset(topic3, constituent == "main-V1"))

m0.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
    + (1+ order + complexity + orderxcomplexity||subj) 
    + (1 + order + complexity + orderxcomplexity||item), 
  subset(topic3,constituent =="main-V1"))
## fail to converge, and fixed-effect matrix shows that 
## 2 coefficients complexity and orderxcomplexity were dropped. 
## So it's best to use "order" as the only fixed effect

m1.MV1 <-lmer(rrt ~ order 
              + (1+ order||subj) 
              + (1 + order ||item), 
              subset(topic3,constituent =="main-V1"))
summary(m1.MV1) # no effect of word order at MV1 (t=-0.134)
```

###check by positions: pos=20 (W9 as reported in the paper)
```{r }
m0.pos20.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
          + (1+ order + complexity + orderxcomplexity||subj) 
           + (1 + order + complexity + orderxcomplexity||item), 
      subset(topic3,position =="20"))
summary(m0.pos20.MV1)

m1.pos20.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
           + (1+ order + complexity + orderxcomplexity||subj) 
           + (1 + complexity + orderxcomplexity||item), 
            subset(topic3,position =="20"))
summary(m1.pos20.MV1)  ### pos20: interaction=3.32, unpack it
```

### main-V2: maximal model overfitted; use Order as the fixed effect 
```{r }
m0.MV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
      + (1+ order + complexity + orderxcomplexity||subj) 
     + (1 + order + complexity + orderxcomplexity||item), 
    subset(topic3,constituent =="main-V2"))
## fail to converge, and fixed-effect matrix shows that
## 2 coefficients complexity and orderxcomplexity were dropped. 
## So it's best to use "order" as the only fixed effect

m1.MV2 <-lmer(rrt ~ order 
              + (1+ order||subj) 
              + (1 + order ||item), 
              subset(topic3,constituent =="main-V2"))
summary(m1.MV2) #no effect of word order at MV2 (t=-1.05)
```

### check pos21 (W10 as reported in the paper)
```{r }
m0.pos21.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order + complexity + orderxcomplexity||subj) 
        + (1 + order + complexity + orderxcomplexity||item), 
        subset(topic3,position =="21"))
summary(m0.pos21.MV1)

m1.pos21.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
        + (1+ order + complexity + orderxcomplexity||subj) 
        + (1 + order + complexity ||item), 
       subset(topic3,position =="21"))
summary(m1.pos21.MV1)  ### ME of order (t=-4.423), ME of complexity (t=-2.188)
```

###Unpack the interaction detected at W9, using nested contrast
```{r }
topic3$TSV_inMC <- ifelse(topic3$condition=="d",-1,
                          ifelse(topic3$condition=="c",1,0)) 
topic3$TSV_inRC <- ifelse(topic3$condition=="b",-1,
                          ifelse(topic3$condition=="a",1,0))

topic3$MC_inSVO <- ifelse(topic3$condition == "b",-1,
                          ifelse(topic3$condition == "d",1,0))
topic3$MC_inTSV <-ifelse(topic3$condition =="a",-1,
                         ifelse(topic3$condition == "c",1,0))
head(topic3, n=5)
```

##### nested comparision pos20.MV1:
```{r }
xtabs(~TSV_inMC + condition,subset(topic3,constituent =="main-V1"))
xtabs(~TSV_inRC + condition,subset(topic3,constituent =="main-V1"))
xtabs(~order + condition, subset(topic3,constituent =="main-V1"))

m0.pos20.MCV1.rrt.nested <-lmer(rrt ~ TSV_inMC + TSV_inRC + complexity 
             + (1 + TSV_inMC + TSV_inRC + complexity||subj) 
           + (1 + TSV_inMC + TSV_inRC + complexity||item),
        subset(topic3,position =="20"), REML = FALSE)

summary(m0.pos20.MCV1.rrt.nested)  ## rrt: t= -3.38, TSV slower than SVO in MC

xtabs(~MC_inSVO + condition, subset(topic3,constituent =="main-V1"))
xtabs(~MC_inTSV + condition, subset(topic3,constituent =="main-V1"))
xtabs(~complexity + condition, subset(topic3,constituent =="main-V1"))


m0.pos20.MCV1.rrt.nested.2<-lmer(rrt~ MC_inSVO + MC_inTSV + order
                + (1 + MC_inSVO + MC_inTSV + order||subj) 
              + (1 + MC_inSVO + MC_inTSV + order||item),
            subset(topic3,position =="20"), REML = FALSE)

summary(m0.pos20.MCV1.rrt.nested.2) ## rrt: t=2.996, in SVO, MC faster than RC
```
