---
title: "Chinese_topic_Exp.2: Statistical Report"
author: "Fuyun Wu "
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chinese topic processing
  - Mandarin: 71id

## Load relevant packages
```{r warning=FALSE}
library(plyr)
library(ggplot2)
library(reshape2)
library(scales) 
library(MASS)
library(lme4)
library(car)
library(languageR)
```

## Import dataset: exp2. without context
```{r }
topic2 <- read.csv("topic2_noContext_71id.csv")
```

```{r }
topic2$subj <- as.factor(topic2$subj)
topic2$item <- as.factor(topic2$item)
```

```{r }
boxcox <- boxcox(topic2$RT~ topic2$condition * topic2$subj) 
##lamda peaks around -1, thus use rrt

topic2 <- subset(topic2, topic2$RT > 50 & topic2$ RT < 5000)
## eliminated 74 (0.36%) datapoints

topic2$rrt <- -1000/topic2$RT
```

## sum-contrast coding
```{r }
order <- ifelse(topic2$condition%in%c("a","c"),-1,1)
complexity <- ifelse(topic2$condition%in%c("a","b"),-1,1)
orderxcomplexity <- ifelse(topic2$condition%in%c("b","c"),-1,1)

topic2$order <- order
topic2$complexity <- complexity
topic2$orderxcomplexity <- orderxcomplexity
head(topic2, n=5)
```

### analyses by word positions
## pos4 (RC-V2): W5
```{r }
m0.pos4.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1 + order + complexity + orderxcomplexity||subj) 
              + (1 + order + complexity + orderxcomplexity||item), 
              subset(topic2,position =="4"))
summary(m0.pos4.RCV2)


m1.pos4.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1 + complexity+ orderxcomplexity ||subj) 
               + (1 + order +complexity + orderxcomplexity||item), 
               subset(topic2,position =="4"))  ## optimal model
summary(m1.pos4.RCV2)
```

### pos4.DE: W6
```{r }
m0.pos5.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
          + (1+ order + complexity + orderxcomplexity||subj) 
          + (1 + order + complexity + orderxcomplexity||item), 
                   subset(topic2,position =="5"))
summary(m0.pos5.DE)

m1.pos5.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
                   + (1+ order ||subj) 
                   + (1 + orderxcomplexity||item), 
                   subset(topic2,position =="5")) ## optimal model
summary(m1.pos5.DE)
```

### pos6.HN: W7
```{r }
m0.pos6.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
           + (1+ order + complexity + orderxcomplexity||subj) 
           + (1 + order + complexity + orderxcomplexity||item), 
          subset(topic2,position =="6"))
summary(m0.pos6.HN)

m1.pos6.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
          + (1+ order + complexity ||subj) 
          + (1 + order + orderxcomplexity||item), 
          subset(topic2,position =="6"))  ##optimal model
summary(m1.pos6.HN)
```

#### pos7.ADV:W8
```{r }
m0.pos7.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
            + (1+ order + complexity + orderxcomplexity||subj) 
            + (1 + order + complexity + orderxcomplexity||item), 
            subset(topic2,position =="7"))
summary(m0.pos7.ADV)

m1.pos7.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
           + (1+ order ||subj) 
           + (1 + order + complexity + orderxcomplexity||item),
           subset(topic2,position =="7")) ## optimal model
summary(m1.pos7.ADV)
```

######pos8.quantifier: W9
```{r }
m0.pos8.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order + complexity + orderxcomplexity||subj) 
              + (1 + order + complexity + orderxcomplexity||item), 
             subset(topic2,position =="8"))
summary(m0.pos8.quantifier)

m0.pos8.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
                 + (1+ order + complexity ||subj) 
                 + (1 + complexity + orderxcomplexity||item), 
                 subset(topic2,position =="8")) ## optimal model
summary(m0.pos8.quantifier)
```

### pos9: W10
```{r }
m0.pos9.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
           + (1+ order + complexity + orderxcomplexity||subj) 
          + (1 + order + complexity + orderxcomplexity||item),  
          subset(topic2,position =="9"))
summary(m0.pos9.MV1)

m1.pos9.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
                    + (1+  complexity ||subj) 
                    + (1 + complexity ||item), 
                    subset(topic2,position =="9")) ## optimal model
summary(m1.pos9.MV1)
```

### pos10: W11
```{r }
m0.pos10.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order + complexity + orderxcomplexity||subj) 
             + (1 + order + complexity + orderxcomplexity||item), 
             subset(topic2,position =="10"))
summary(m0.pos10.MV1)

m1.pos10.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
                     + (1+ order ||subj) 
                     + (1 + complexity + orderxcomplexity||item), 
                     subset(topic2,position =="10")) ## optimal model
summary(m1.pos10.MV1)
```

## analyses by part of speech 
### RC-V2: 
```{r }
m0.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
                + (1+ order + complexity + orderxcomplexity||subj) 
                + (1 + order + complexity + orderxcomplexity||item), 
                subset(topic2,constituent =="RC-V2"))
summary(m0.RCV2)

m1.RCV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
                + (1+ order + orderxcomplexity||subj) 
                + (1 + complexity ||item), 
                subset(topic2,constituent =="RC-V2")) ## optimal model
summary(m1.RCV2)
```

## DE: 
```{r }
m0.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order + complexity + orderxcomplexity||subj) 
              + (1 + order + complexity + orderxcomplexity||item), 
              subset(topic2,constituent =="DE"))
summary(m0.DE)

m1.DE <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order ||subj) 
              + (1 + order + complexity + orderxcomplexity||item), 
              subset(topic2,constituent =="DE")) ## optimal model
summary(m1.DE)
```

### HN: 
```{r }
m0.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order + complexity + orderxcomplexity||subj) 
              + (1 + order + complexity + orderxcomplexity||item), 
              subset(topic2,constituent =="HN"))
summary(m0.HN)

m1.HN <- lmer(rrt ~ order + complexity + orderxcomplexity 
              + (1+ order + complexity ||subj) 
              + (1 + order + complexity + orderxcomplexity||item), 
              subset(topic2,constituent =="HN"))
summary(m1.HN)
```

### ADV: 
```{r }
m0.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ order + complexity + orderxcomplexity||subj) 
               + (1 + order + complexity + orderxcomplexity||item), 
               subset(topic2,constituent =="ADV"))
summary(m0.ADV)

m1.ADV <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ order + complexity ||subj) 
               + (1 + order + complexity + orderxcomplexity||item), 
               subset(topic2,constituent =="ADV")) ## optimal model
summary(m1.ADV)
```

### quantifier: 
```{r }
m0.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ order + complexity + orderxcomplexity||subj) 
               + (1 + order + complexity + orderxcomplexity||item), 
               subset(topic2,constituent =="quantifier"))
summary(m0.quantifier)

m1.quantifier <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ order + complexity ||subj) 
               + (1 + order + complexity + orderxcomplexity||item), 
              subset(topic2,constituent =="quantifier")) ## optimal model
summary(m1.quantifier)
```

### main-V1  ## ME of order, ME of complexity, and interaction
```{r }
m0.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
            + (1+ order + complexity + orderxcomplexity||subj) 
           + (1 + order + complexity + orderxcomplexity||item), 
           subset(topic2,constituent =="main-V1"))
summary(m0.MV1)

m1.MV1 <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ complexity ||subj) 
               + (1 + complexity ||item), 
               subset(topic2,constituent =="main-V1")) ## optimal model
summary(m1.MV1)
```

### main-V2: ME of order, ME of complexity, interactions
```{r }
m0.MV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ order + complexity + orderxcomplexity||subj) 
               + (1 + order + complexity + orderxcomplexity||item), 
               subset(topic2,constituent =="main-V2"))
summary(m0.MV2)

m1.MV2 <- lmer(rrt ~ order + complexity + orderxcomplexity 
               + (1+ order + complexity + orderxcomplexity||subj) 
               + (1 + order + complexity||item), 
               subset(topic2,constituent =="main-V2")) ## optimal model
summary(m0.MV2)
```

##Unpack the interactions at MV1 & MV2
## nested contrast
```{r }
topic2$TSV_inMC <- ifelse(topic2$condition=="d",-1,
                          ifelse(topic2$condition=="c",1,0)) 
topic2$TSV_inRC <- ifelse(topic2$condition=="b",-1,
                          ifelse(topic2$condition=="a",1,0))

topic2$MC_inSVO <- ifelse(topic2$condition == "b",-1,
                          ifelse(topic2$condition == "d",1,0))
topic2$MC_inTSV <-ifelse(topic2$condition =="a",-1,
                         ifelse(topic2$condition == "c",1,0))
head(topic2, n=5)
```

##### nested comparision MV1:
```{r }
m0.MCV1.rrt.nested <-lmer(rrt ~ TSV_inMC + TSV_inRC + complexity 
               + (1 + TSV_inMC + TSV_inRC + complexity||subj) 
               + (1 + TSV_inMC + TSV_inRC + complexity||item),
             subset(topic2,constituent =="main-V1"), REML = FALSE)

summary(m0.MCV1.rrt.nested)  ###  t=4.33, TSV slower than SVO in MC


m0.MCV1.rrt.nested.2<-lmer(rrt~ MC_inSVO + MC_inTSV + order
              + (1 + MC_inSVO + MC_inTSV + order||subj) 
             + (1 + MC_inSVO + MC_inTSV + order||item),
          subset(topic2,constituent =="main-V1"), REML = FALSE)

summary(m0.MCV1.rrt.nested.2) ##  t=-4.43, in SVO, MC faster than RC
```

# nested comparison # MCV2
```{r }
m0.MCV2.rrt.nested <-lmer(rrt ~ TSV_inMC + TSV_inRC + complexity 
             + (1 + TSV_inMC + TSV_inRC + complexity||subj) 
            + (1 + TSV_inMC + TSV_inRC + complexity||item),
          subset(topic2,constituent =="main-V2"), REML = FALSE)

summary(m0.MCV2.rrt.nested)  ###  t=12.99, TSV slower than SVO in MC


m0.MCV2.rrt.nested.2<-lmer(rrt~ MC_inSVO + MC_inTSV + order
         + (1 + MC_inSVO + MC_inTSV + order||subj) 
         + (1 + MC_inSVO + MC_inTSV + order||item),
         subset(topic2,constituent =="main-V2"), REML = FALSE)

summary(m0.MCV2.rrt.nested.2) ##  t=-13.89, in SVO, MC faster than RC
```
