---
title: "Chinese_topic_Exp.1: Statistical Report"
author: "Fuyun WU "
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chinese topic processing
  - Mandarin: 32id

## Load relevant packages
```{r warning=FALSE}
library(plyr)
library(ggplot2)
library(reshape2)
library(scales) 
library(MASS)
library(lme4)
library(car)
library(languageR)
```

## Import dataset, and make variables as factors
```{r }
topic <- read.csv("topic1_32id.csv")
```

```{r }
topic$subj <- as.factor(topic$subj)
topic$item <- as.factor(topic$item)
```

```{r }
boxcox(topic$RT~topic$condition) 
##lamda peaks around -1, thus use rrt

topic$rrt <- -1000/topic$RT
topic <- subset(topic, topic$RT > 50 & topic$ RT < 5000)
## eliminated 11 datapoints
```

##statistical analyses by Word region (W)
### at W5 (region =4 (MV vs. agent-NP)
```{r warning=FALSE} 
m.W5 <-lmer(rrt~order + (1+order||subj) + (1+order||item), 
            subset(topic, region =="4")) ## fail to converge
m1.W5 <-lmer(rrt~order + (1+order||subj) + (1|item), 
             subset(topic, region =="4")) ##fail to converge
m2.W5 <-lmer(rrt~order + (1|subj) + (1|item), 
             subset(topic, region =="4"))

summary(m2.W5)   # t=2.694
```

### at W6 (region=5, DCL vs. quantifier):
```{r warning=FALSE} 
m.W6 <-lmer(rrt~order + (1+order||subj) + (1+order||item), 
            subset(topic, region =="5"))##fail to converge
m1.W6 <-lmer(rrt~order + (1+order||subj) + (1|item), 
             subset(topic, region =="5")) ##fail to converge
m2.W6 <-lmer(rrt~order + (1|subj) + (1|item),
             subset(topic, region =="5"))## optimal model
summary(m2.W6)
```

### at W7 (region = 6, patient-NP vs. MV)
```{r warning=FALSE} 
m.W7 <-lmer(rrt~order + (1+order||subj) + (1+order||item),
            subset(topic, region =="6"))##fail to converge
m1.W7 <-lmer(rrt~order + (1+order||subj) + (1|item),
            subset(topic, region =="6"))##fail to converge
m2.W7 <-lmer(rrt~order + (1|subj) + (1|item),
             subset(topic, region =="6"))
summary(m2.W7)  
```

### at W8 (region=7, spillover1, e.g., 'but')
```{r warning=FALSE} 
m.W8 <-lmer(rrt~order + (1+order||subj) + (1+order||item),
            subset(topic, region =="7"))##fail to converge
m1.W8 <-lmer(rrt~order + (1+order||subj) + (1|item),
             subset(topic, region =="7"))
summary(m1.W8) 
```

### at W9 (region=8, spillover2, e.g. bu yiding 'not')
```{r warning=FALSE} 
m.W9 <-lmer(rrt~order + (1+order||subj) + (1+order||item), 
            subset(topic, region =="8"))##fail to converge
m1.W9 <-lmer(rrt~order + (1+order||subj) + (1|item), 
             subset(topic, region =="8"))##fail to converge
m2.W9 <-lmer(rrt~order + (1|subj) + (1|item), 
             subset(topic, region =="8")) 
summary(m2.W9) 
```

### W10 (region=9, spillover3)
```{r warning=FALSE} 
m.W10 <-lmer(rrt~order + (1+order||subj) + (1+order||item), 
             subset(topic, region =="9"))
m1.W10 <-lmer(rrt~order + (1+order||subj) + (1|item), 
              subset(topic, region =="9"))
m2.W10 <-lmer(rrt~order + (1|subj) + (1|item), 
              subset(topic, region =="9"))## optimal model
summary(m2.W10)
```

## statistical analyses by part of speech (POS)
##  POS = quantifier (d2, e.g. 'every')
```{r warning=FALSE} 
m.quantifier <-lmer(rrt~order+(1+order||subj)+(1+order||item),
                    subset(topic, position =="d2"))
m1.quantifier <-lmer(rrt~order+(1+order||subj)+(1|item),
                     subset(topic, position =="d2"))## optimal model
summary(m1.quantifier)
```

##  POS = agent-NP ('student')
```{r warning=FALSE} 
m.agent <-lmer(rrt~order+(1+order||subj)+(1+order||item),
               subset(topic, position =="na"))
m1.agent <-lmer(rrt~order+(1+order||subj)+(1|item),
                subset(topic, position =="na"))
m2.agent <-lmer(rrt~order+(1|subj)+(1|item),
                subset(topic, position =="na"))## optimal model
summary(m2.agent)  
```

## POS = patient-NP ('Tang-poem')
```{r warning=FALSE} 
m.patient <-lmer(rrt~order + (1+order||subj) + (1+order||item), 
                 subset(topic, position =="np"))
m1.patient <-lmer(rrt~order + (1+order||subj) + (1|item), 
                  subset(topic, position =="np"))
m2.patient <-lmer(rrt~order + (1|subj) + (1|item), 
                  subset(topic, position =="np"))## optimal model
summary(m2.patient) 
```

## POS = MV ('can-recite')
```{r warning=FALSE} 
m.MV <-lmer(rrt~order+(1+order||subj)+(1+order||item),
            subset(topic, position =="v"))
m1.MV <-lmer(rrt~order+(1+order||subj)+(1|item),
             subset(topic, position =="v"))
m2.MV <-lmer(rrt~order+(1|subj)+(1|item),
             subset(topic, position =="v"))## optimal model
summary(m2.MV)    
```
